\documentclass[8pt,a4paper]{article}
\usepackage[left=0.3in,top=0.2in,right=0.3in,bottom=0.2in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}
\usepackage{tabularx}
\usepackage{parskip}

% Remove page numbering
\pagestyle{empty}

% Color definitions
\definecolor{primarycolor}{RGB}{0, 102, 204}
\definecolor{secondarycolor}{RGB}{64, 64, 64}
\definecolor{accentcolor}{RGB}{0, 153, 76}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=primarycolor,
    filecolor=primarycolor,
    urlcolor=primarycolor,
}

% Custom section formatting
\titleformat{\section}
{\color{primarycolor}\small\bfseries}
{}
{0em}
{}[\vspace{-0.02em}\titlerule\vspace{0.02em}]

\titleformat{\subsection}
{\color{secondarycolor}\small\bfseries}
{}
{0em}
{}

% Custom commands
\newcommand{\cvheader}[1]{%
    \begin{center}
        {\Large\bfseries\color{primarycolor} #1}
    \end{center}
}

\newcommand{\contactinfo}[1]{%
    \begin{center}
        \small #1
    \end{center}
    \vspace{0.02em}
}

\newcommand{\cventry}[4]{%
    \textbf{#1} \hfill {\small\color{secondarycolor} #2} \hfill {\footnotesize\textit{#3}}\\
    #4
    \vspace{0.02em}
}

\newcommand{\skillsection}[2]{%
    \textbf{#1:} #2\\[-0.02em]
}

% Set list formatting
\setlist{nosep, leftmargin=0.8em, itemsep=-0.02em}

\begin{document}

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------

\cvheader{Ramez Nashaat Lahzy}

\contactinfo{
\faEnvelope\ \href{mailto:lahzyramez@gmail.com}{lahzyramez@gmail.com} \quad
\faPhone\ (+20) 1550575832 \quad
\faMapMarker\ Cairo, Egypt \\
\faGithub\ \href{https://github.com/ramezlahzy}{github.com/ramezlahzy} \quad
\faLinkedin\ \href{https://linkedin.com/in/ramez-lahzy-37188021a/}{LinkedIn} \quad
\faGlobe\ \href{https://www.upwork.com/freelancers/ramezn3}{Upwork} \quad
\faCode\ \href{https://codeforces.com/profile/Ramez__}{Codeforces: 1657}
}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------

\section{Professional Summary}

 Full-Stack Engineer with 2+ years building scalable React/React Native apps and AWS infrastructure. 25+ projects completed on Upwork, with 5.0/5.0 rating, \$8,000+ revenue, and 10,000+ users served. ECPC Top 10, Codeforces Expert (1657), Top 3\% Upwork.


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{German University in Cairo (GUC)}{Oct 2020 - July 2025}{Bachelor of Computer Science and Engineering}{
\textbf{CGPA:} 1.22 (German Scale - Grade A) \\
\textbf{Thesis:} SAT Solving Algorithms at Ulm University, Germany (Grade: A+)
}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS & CERTIFICATIONS
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------
% -----------------------
% INSIDE YOUR DOCUMENT
% -----------------------

% ----------- PROFESSIONAL EXPERIENCE ------------

\section{Professional Experience}

\cventry{Full-Stack Developer}{Subbie Company}{Sept 2024 - Present}{Remote, Australia}{}{
\begin{itemize}
    \item Delivered 1,200+ hours of full-stack development for a scalable SaaS survey system using AWS CDK, Lambda, DynamoDB, Cognito, and React.
    \item Architected cloud-native infrastructure (IaC, serverless) using AWS services and CI/CD pipelines; applied Builder and Observer patterns.
    \item Integrated LLMs (OpenAI, Claude) with ChromaDB for real-time NLP insights and automated analytics workflows.
\end{itemize}
}

\cventry{Full-Stack Developer}{Pyng Technologies}{Jan 2024 - April 2024}{Remote, London, UK}
\begin{itemize}
    \item Developed a React Native Android app using NFC and Accessibility APIs to enable contactless payments and peer-to-peer transfers.
    \item Built native Android modules and Node.js backend; followed clean architecture, repository pattern, and TypeScript best practices.
\end{itemize}

\cventry{Game Developer Intern}{Gmind Studio}{July 2022 - Sept 2022}{Cairo, Egypt}{}{
\begin{itemize}
    \item Built a Unity-based 3D educational game with backend integration using C\#, OOP, Firebase Realtime DB, REST APIs, and cloud storage.
\end{itemize}
}

% ----------- KEY PROJECTS ------------

\section{Key Projects}

\cventry{Enterprise Microservices Platform}{2025}{Spring Boot, Kubernetes, Redis, RabbitMQ}
Designed and deployed a distributed social platform using Nginx API gateway, Docker containers, and RabbitMQ messaging. CI/CD and Helm used in Kubernetes orchestration. \href{https://github.com/mariamhmostafa/FinalProject-29-Cache_Me_If_You_Can}{GitHub}

\cventry{Healthcare Management Ecosystem}{2024}{MERN Stack, MongoDB, TypeScript}
Full-stack web system using MongoDB, React, Express.js, and Node.js with real-time dashboards for clinics and pharmacies serving 10K+ users. \href{https://github.com/advanced-computer-lab-2023/Copilot-and-Sons-Clinic}{Clinic} | \href{https://github.com/advanced-computer-lab-2023/Copilot-and-Sons-Pharmacy}{Pharmacy}

\cventry{AWS CDK Full Stack Infrastructure}{2024}{AWS Lambda, DynamoDB, CodePipeline}
Built production-grade infrastructure-as-code stack using AWS CDK, integrating CI/CD pipelines, authentication, and serverless business logic. \href{https://github.com/ramezlahzy/cdk_fullstack_app}{GitHub}

\cventry{SubReach – YouTube Engagement Booster}{2025}{Flutter, Next.js, Firebase, Firestore, Stripe, GCP}
Built a YouTube automation platform that generates fake likes and subscriptions using the YouTube API. Integrated Stripe for selling point-based campaigns. Developed cross-platform mobile app with Flutter, serverless backend using Firebase Functions, and admin dashboard with Next.js.
\href{https://github.com/ramezlahzy/SubReach}{GitHub}


% \section{Technical Skills}

% \skillsection{Programming}{JavaScript/TypeScript, Java, Python, C++, C\#, SQL, HTML5, CSS3}
% \skillsection{Frontend \& Mobile}{React.js, React Native, Next.js, Vue.js, Bootstrap, Tailwind CSS, Material-UI}
% \skillsection{Backend \& Cloud}{Node.js, Express.js, Spring Boot, AWS (Lambda, DynamoDB, S3, CDK), Docker, Kubernetes, Nginx}
% \skillsection{Databases \& Tools}{MongoDB, PostgreSQL, Redis, RabbitMQ, Firebase, Git, Jenkins, Postman, Unity 3D, Jest}
\section{Achievements \& Certifications}
\begin{itemize}
    \item \textbf{Academic:} Top 1.3\% at GUC, 2nd in high school governorate
    \item \textbf{Scholarship:} Full merit award at German University in Cairo
    \item \textbf{Competitive Programming:} ECPC 7th place, Codeforces 1657, 1K+ problems
    \item \textbf{Freelancing:} Top 3\% on Upwork, \$8K+, 25+ projects, 1,200+ hours
    \item \textbf{Research:} Co-authored paper on SAT solver optimizations
\end{itemize}

\section{Additional Information}

\skillsection{Languages}{Arabic (Native), English (Advanced C1), German (Intermediate B2)}

\end{document}
